---
title: "CARPS Reproducibility Report"
output:
  html_document:
    toc: true
    toc_float: true
---

#### Article ID: 11-12-2014 PS
#### Pilot 1: Michael Ko
#### Co-pilot: Danielle Boles
#### Start date: 10/27/17
#### End date: 11/3/17

-------

#### Methods summary: 
In study 1, 150 introductory psychology students were randomly assigned to a "real" or a "hypothetical" condition. In the real condition, participants believed that they would have a real opportuniy to connect with potential romantic partners. In the hypothetical condition, participants simply imagined that they are on a date. All participants were required to select their favorite profile and answer whether they were willing to exchange contact information. 

------

#### Target outcomes: 
We next tested our primary hypothesis that participants would be
more reluctant to reject the unattractive date when they
believed the situation to be real rather than hypothetical.
Only 10 of the 61 participants in the hypothetical condition
chose to exchange contact information with the
unattractive potential date (16%). In contrast, 26 of the
71 participants in the real condition chose to exchange
contact information (37%). A chi-square test of independence
indicated that participants were significantly less
likely to reject the unattractive potential date in the real
condition compared with the hypothetical condition,
X^2(1, N = 132) = 6.77, p = .009.

------

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
```

## Step 1: Load packages

```{r}
library(tidyverse) # for data munging
library(knitr) # for kable table formating
library(haven) # import and export 'SPSS', 'Stata' and 'SAS' Files
library(readxl) # import excel files
library(CARPSreports) # custom report functions
library(broom)
library(labelled)# converts SPSS's labelled to R's factor 
```

## Step 2: Load data

```{r}
# We are only looking into Study 1
d <- read_sav('./data/Empathy Gap Study 1 data.sav')
```

## Step 3: Tidy data

```{r}
d_tidy <- d %>% select(condition, exchangeinfo)
d_tidy$condition <- to_factor(d_tidy$condition)
d_tidy$exchangeinfo <- to_factor(d_tidy$exchangeinfo)
```

## Step 4: Run analysis

### Descriptive statistics

We will first attempt to reproduce the number and percentage of participants who 
exchange contact information in both conditions.

> Only 10 of the 61 participants in the hypothetical condition
chose to exchange contact information with the
unattractive potential date (16%). In contrast, 26 of the
71 participants in the real condition chose to exchange
contact information (37%).

```{r}
kable(table(d_tidy$condition, d_tidy$exchangeinfo))

mean <- d_tidy %>% group_by(condition) %>% summarise(mean = 1 - mean(as.numeric(exchangeinfo) - 1))
kable(mean)
```

Looks exactly on point.

### Inferential statistics

Next we will try to reproduce the chi squared test examining significance of 
conditional difference in exchacnging contact information.

> A chi-square test of independence
indicated that participants were significantly less
likely to reject the unattractive potential date in the real
condition compared with the hypothetical condition,
X^2(1, N = 132) = 6.77, p = .009.

```{r}
test <- chisq.test(d_tidy$condition, d_tidy$exchangeinfo, correct = FALSE)
kable(tidy(test))
```

Looks exactly on point.

## Step 5: Conclusion

```{r}
carpsReport(Report_Type = 'pilot',
          Article_ID = 'CARPS_11-12-2014_PS', 
          Insufficient_Information_Errors = 0,
          Decision_Errors = 0,
          Major_Numerical_Errors = 0,
          Time_to_Complete = 60, 
          Author_Assistance = FALSE)
```

The final outcome was a success. Our findings yielded the same descriptive and inferrential statistics at the original paper.

```{r session_info, include=TRUE, echo=TRUE, results='markup'}
devtools::session_info()
```
